Performance of two different ontological and data access methods

### 2014-07-03 cold2014/magnus.tex
Running the experiment er trimmet
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@718 43ef1190-90fd-4dd7-a769-d0121f02b80e

\documentclass{llncs}
%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}

@@

\begin{table}
\begin{center}
    \begin{tabular}{ | l | l  l  l |}
    \hline
    {\bf Run} &  {\bf Fuel type} & {\bf Transmission} & {\bf Speed} \\ \hline
	 1 & Diesel & Automatic & 100 \\ \hline
	 2 & Petrol & Automatic & 100 \\ \hline
	 3 & Diesel & Manual & 100 \\ \hline
	 4 & Petrol & Manual & 100 \\ \hline
	 5 & Diesel & Automatic & 200 \\ \hline
	 6 & Petrol & Automatic & 200 \\ \hline
	 7 & Diesel & Manual & 200 \\ \hline
	 8 & Petrol & Manual &  200 \\ \hline
    \end{tabular}
\end{center}
\caption{A filled planning matrix with 3 factors}\label{designsspec}
\end{table}

@@

In the experiments the definition for VSO/COO is \textsf{-vso} and for
CO is \textsf{-co}.  These two definitions stand for which ontology
are tested in a particular run. In practice this means that when we
send in the keyword \textsf{-vso} we only run the specification search
against the car models represented by VSO/COO, in our case the data
from Daimler. This is referred to as the ontology factor in each
experiment and is a factor in all the experiments which are presented
in this thesis. The ontology factor represents the difference in how
the data are represented and how the ontologies are structures, and
with this factor we want to determine how this affects the overall
performance.  We have programmed the application so that the querying
of the ontologies are done as similar as possible on both levels. This
was done to eliminate any interference from the application. There are
some differences in the programming due that the ontologies were
different and they will be discussed later on.  In Chapter
\ref{prototype}, the application and its differences are explained in
depth.

Before starting on the experiment we had to find a way to do the
actual experiment. We wanted to first create the planning matrix and
then execute each run as a HTTP post. To do this we needed to make a
small script to calculate the $2^k$ runs and perform the HTTP
posts. We chose to use the programming language \emph{python} to do
this. That was because python was a familiar language and it also had
a package for DoE\footnote{http://pythonhosted.org/pyDOE/}. With the
DoE package we just declared the amount of factors and the matrix was
created. At that point the matrix looked more like Table
\ref{designs}, which meant that we had to substitute the + and - with
the levels of each factor.  Further in the script we used the package
\textsf{request}\footnote{http://requests.readthedocs.org/en/latest/}
to do the HTTP posts in python. Below one can see the line of code
executing the request.

@@

All of the planning matrices, graphs and results will be presented
with each experiment later on in this section.  The discussion and
interpretation of the results will be presented in Chapter
\ref{Discussion}.  Before starting the experiments we will present
abbreviations for each factor because their full name made the graphs
totally illegible. These abbreviations will be used in the graphs and
tables further on in this section.  The results from all the
experiments can be found in appendix \ref{appD}.
\begin{itemize}
  \item Ontology = O
  \item Fuel Type = FT
  \item Transmission = T
  \item Weight = W
  \item Total Weight = WT
  \item Emission = E
  \item Nr. of Gears = G
  \item Seating Capacity = SC
  \item Fuel Consumption = FC
  \item Doors = D
\end{itemize}

>>>>

\documentclass{llncs}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}

@@

%\begin{table}
%\begin{center}
%    \begin{tabular}{ | l | l  l  l |}
%    \hline
%    {\bf Run} &  {\bf Fuel type} & {\bf Transmission} & {\bf Speed} \\ \hline
%	 1 & Diesel & Automatic & 100 \\ \hline
%	 2 & Petrol & Automatic & 100 \\ \hline
%	 3 & Diesel & Manual & 100 \\ \hline
%	 4 & Petrol & Manual & 100 \\ \hline
%	 5 & Diesel & Automatic & 200 \\ \hline
%	 6 & Petrol & Automatic & 200 \\ \hline
%	 7 & Diesel & Manual & 200 \\ \hline
%	 8 & Petrol & Manual &  200 \\ \hline
%    \end{tabular}
%\end{center}
%\caption{A filled planning matrix with 3 factors}\label{designsspec}
%\end{table}

@@

In the experiments the definition for VSO/COO is \textsf{-vso} and for
CO is \textsf{-co}.  These two definitions stand for which ontology
are tested in a particular run. In practice this means that when we
send in the keyword \textsf{-vso} we only run the specification search
against the car models represented by VSO/COO, in our case the data
from Daimler. This is referred to as the ontology factor in each
experiment and is a factor in all the experiments which are presented
in this thesis. The ontology factor represents the difference in how
the data are represented and how the ontologies are structures, and
with this factor we want to determine how this affects the overall
performance.  We have programmed the application so that the querying
of the ontologies are done as similar as possible on both levels. This
was done to eliminate any interference from the application.

First we wanted to create the planning matrix and
then execute each run as a HTTP post. To do this we needed to make a
small script to calculate the $2^k$ runs and perform the HTTP
posts. We chose to use the programming language \emph{python} to do
this. That was because python was a familiar language and it also had
a package for DoE\footnote{http://pythonhosted.org/pyDOE/}. With the
DoE package we just declared the amount of factors and the matrix was
created.  Further in the script we used the package
\textsf{request}\footnote{http://requests.readthedocs.org/en/latest/}
to do the HTTP posts in python. Below one can see the line of code
executing the request.

@@

Before starting the experiments we will present
abbreviations for each factor because their full name made the graphs
totally illegible. The results from all the
experiments can be found in appendix \ref{appD}. %TODO: What to do with the appendix?
\begin{itemize}
  \item Ontology = O
  \item Fuel Type = FT
  \item Transmission = T
  \item Weight = W
  \item Total Weight = WT
  \item Emission = E
  \item Nr. of Gears = G
  \item Seating Capacity = SC
  \item Fuel Consumption = FC
  \item Doors = D
\end{itemize}
